Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-02-11 latex/comp_or.tex
data100 almost finished
Results updated on latex

We ran Algorithm \ref{alg:main} in the 6 scenarios described in Table \ref{tab:scenarios}, considering 3 methods for node-by-node resolution: {\it Gurobi}, {\it Shims} (Algorithm \ref{alg:shims}), and {\it mpShims} (Algorithm \ref{alg:mpshims}).

@@

\midrule
\multirow{7}{*}{$2.0$}&\multirow{2}{*}{ $Gurobi$}& $f$                & 16.49       & {\bf 11.60} & {\bf 16.68} & 18.33       &  20.10      & 17.94        &   \\%
&                                                & {\it run-time (s)} &  12         &   25        &  45         &  169        &   437       &  2377        &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 12.53       &  8.31       &  10.04      &  10.94      &   11.72     & 10.13        & \\%
&                                                & {\it run-time (s)} &  < 1        &  3          &    6        &   24        &   70        &  419         &\\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & {\bf 16.71} & 10.86       & {\bf 16.68} & {\bf 18.84} & {\bf 21.30} & {\bf 19.39}  &   \\%
&                                                & {\it run-time (s)} &  < 1        &  2          &    3        &   9         &   26        &   158        &   \\%

@@

For {\it Gurobi} in some scenarios, less than 50\% of the results were optimal, and the remaining were suboptimal due to the time limit. This explains that {\it mpShims} surpassed {\it Gurobi} results.

>>>>

We ran Algorithm \ref{alg:main} in the 6 scenarios described in Table \ref{tab:scenarios}, considering 3 methods for node-by-node resolution: the {\it Gurobi} MIP solver, {\it Shims}, and {\it mpShims} (Algorithm \ref{alg:mpshims}).

@@

\midrule
\multirow{7}{*}{$2.0$}&\multirow{2}{*}{ $Gurobi$}& $f$                & 24.04       & {\bf 17.33} & 24.62       & {\bf 26.36} &  28.88      & 25.89        & 0.98  \\%14962
&                                                & {\it run-time (s)} &  14         &   34        &  62         &  236        &   609       & 3431         & 1.0  \\%4386

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 18.41       &  13.37       &  15.90      &  16.17      &   17.08     & 15.96        & 0.65 \\%
&                                                & {\it run-time (s)} &  < 1        &  4          &    7        &   30         &   85        &  501         & 7.0 \\%628

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & {\bf 24.28} & 16.54       & {\bf 25.53} & 25.87        & {\bf 29.10} & {\bf 27.02}  & {\bf 0.99} \\%
&                                                & {\it run-time (s)} &  < 1        &  2          &    3        &   12         &   32        &   188        & {\bf 18.4}  \\%238

@@

For the MIP solver in some scenarios, less than 50\% of the results were optimal, and the remaining were suboptimal due to the time limit. This explains that {\it mpShims} surpassed the MIP solver results.

In \cite{MesquitaSanches2023}, {\it Shims} surpassed the MIP solver, on average, because the time limit they used (0.7s) was sufficient to guarantee a worst-case solution in less than 30min. This decision caused most of the MIP solver results to be poor. In this work, we used as a time limit the worst {\it Shims} run-time, which was 1.8s. This made the MIP solver yield optimal or near-optimal solutions. This is good for the reader to have an idea of the real performance differences among the methods.

{\it mpShims} presented the best performance, as it was slightly better in terms of quality than the MIP solver, and 15 times faster on average.
